Vragenlijst thesis evaluatie

### 2015-08-09 doc/template/chap-4.tex
verbeteringen Jeroen nog

\section{Models for worm propagation}
\label{modelsforpropagation}
To use the models for worm propagation in our model of the FlipIt game it is sufficient to know the propagation speed of the worm and define after how many time units a sufficient number of nodes in the network are infected. This will be equal to the \textit{d} parameter in our FlipIt model. \\

%Scan based or Topology based
A node in a network can be in three different states: susceptible, infected or removed. A susceptible node is a node that is vulnerable to infection. An infected node is a node that has been compromised and can infect other nodes. A removed node is dead or immune, which means it cannot be infected again by worms. With these three states three main propagation models are proposed: SI, SIR and SIS. SI model is a model where a node once infected stays infected. In an SIR model a node can once it is infected become removed. In an SIS model a node can become again susceptible after it has been infected. Based on these three models various other models have been proposed. We are only interested in models where we can find the time that it takes for a worm to infect a sufficient amount of nodes.
Table \ref{tree} gives an overview of the most common propagation methods with the given type. This table comes from the most recent survey \citep{wang2014modeling}, which encompasses results of older surveys. Moreover, the survey explicitly focuses on propagation methods, while other papers also focus on other aspects such as  detection mechanisms and containment systems. All models that are based on SI model type (Susceptible-Infected) are good, because in our model every node that is infected will stay infected. Only models Local Preference and Email worms model will not be explained because it involves human interaction. OSN model is done by means of simulation. The SIR AAWP model is also interesting to explain because the parameter that involves the R part of the model can be deleted.  \\

>>>>

\section{Models for worm propagation}
\label{modelsforpropagation}
To use the models for worm propagation in the model of the FlipIt game with propagation delay it is sufficient to know the propagation speed of the worm and determine after how many time units a sufficient number of nodes in the network is infected. This will be equal to the \textit{d} parameter in our FlipIt model. \\

%Scan based or Topology based
A node in a network can be in three different states: susceptible, infected or removed. A susceptible node is a node that is vulnerable to infection. An infected node is a node that has been compromised and can infect other nodes. A removed node is dead or immune, which means it cannot be infected again by worms. With these three states three main propagation models are proposed: SI, SIR and SIS. In the SI model, a node that has once been infected, stays infected. In the SIR model, an infected node can be removed afterwards. This node cannot become infected again. In the SIS model a node can become susceptible again after it has been infected. Based on these three models various other models have been proposed. \todo{referenties naar andere modellen} We are only interested in models that will allow us to find the time required for a worm to infect a sufficient amount of nodes.
Table \ref{tree} gives an overview of the most common propagation methods with the given type. This table comes from the most recent survey \citep{wang2014modeling}, which encompasses results of older surveys. Moreover, the survey explicitly focuses on propagation methods, while other papers also focus on other aspects such as  detection mechanisms and containment systems. All models that are based on SI model type (Susceptible-Infected) are good, because in our model every node that is infected will stay infected. Only the Local Preference and Email worms models will not be explained because they involve human interaction. OSN model is done by means of simulation. The SIR AAWP model is also interesting because the parameter that involves the R part of the model can be deleted.  \\ \todo{laatste zinnen zijn wazig: Het deel erboven over SIS enzo was duidelijk maar hier worden andere modellen er bij de haren bijgesleurd. Als we die niet bekijken, gewoon kort zeggen dat er andere modellen zijn (e.g. SIR AAWP, Email worms, ....) maar dat deze niet worden bekeken ofzo?}
